Profit Optimisation in Heterogeneous 2-link Parallel Games

### 2024-12-27 thesis/article.tex
Thesis: Final fixes in Chapter 3, fixes from Th. Lianeas notes, rewordings

\thispagestyle{empty}
\pagenumbering{gobble}
\chapter*{Abstract}
In this masters thesis we study a $2$-level game where, on an $n$-link network from a source $s$ to a target $t$, a unit of flow wants to move from $s$ to $t$ using the link with the lowest cost, while the link operators compete for profit by assigning tolls to links and thus creating a toll congestion game.
We examine only affine latencies for the links.
In addition, each flow user responds to tolls in a heterogeneous way, i.e. each player $p$ in the flow has a different money-time sensitivity value, which is described by a distribution function $\alpha(p)$.
We first present some definitions and properties of pricing homogeneous games, heavily based on previous work, and using them as base, we extend them to describe pricing games with heterogeneous users.
We introduce a new term, the sensitivity split function $\as(t)$, defined for any $2$ links of the network as the time-money sensitivity value for which, given a set of tolls $t$, the link costs are equal.
With the help of $\as$ we describe some properties around the selfish behaviour of heterogeneous users for different tolls, as well as prove the existence of bounds for the sensitivity values that are relevant to the game.
Then, arriving at the main body of this study, we investigate the existence of a Nash Equilibrium in the profit game between the link operators for different cases of heterogeneous users.
We show there is no Nash Equilibrium when there are many users with $0$ sensitivity, i.e. players not affected by tolls, so we further assume $\alpha(p) > 0$.
We then investigate cases of fixed distribution functions, which, even though create homogeneous behaviour for the users (making them pseudo-heterogeneous games), help us describe how flow, tolls and equilibria behave as that fixed value changes.
Using all the above, we study step distribution functions, where by limiting our scope to $2$ links, we present strict conditions necessary for the existence or not of a Nash Equilibrium in the profit game between the link operators.
We present and analyse an algorithm to calculate that equilibrium, if it exists, and finish with some discussion about potential future work.
\clearpage

@@

In this thesis we study a two level game.
On the basis there is a network with 2 nodes $(s, t)$ and $n$ links, each link directed from $s$ to $t$ and weighted by a non-decreasing latency function that defines how the traffic increases as more players flow into that link.
On the lower level, a flow $[0, 1]$ wants to move from $s$ to $t$ using one of the $n$ links and experience minimum latency (traffic).
On the upper level, each link is managed by a different operator who can assign a toll to their link and gain profit proportional to that toll and the flow that ends up using the link.
The tolls impose an additional cost to the flow players, affecting the lower level game, and the link operators compete with each other to maximise their profit.
In our case we will additionally assume that the flow users behave in a heterogeneous way when it comes to tolls, meaning that each player has a different money-time trade-off and thus see the link costs differently.

The structure of this thesis is as such.
We finish this chapter by briefly presenting previous work in this field, all while examining some of the different models and properties that have been researched in the literature so far.
This will also serve as a bridge to Chapter \ref{chapter:preliminaries} were we will set our basis for the rest of the study.
This includes formal definitions of the models and properties we introduced from previous work as well as some additional -but still basic- properties of the models, with heavy focus on the money-time user sensitivity, captured by a distribution function $\alpha$.

Entering the main body of our work, in Chapter \ref{chapter:split} we introduce a new term regarding any two links of the network, called \textit{money-time sensitivity split}, which captures the notion of a (potentially non-existent) player whose money-time sensitivity makes them view the two links as equal.
We will then analyse that notion and provide properties and bounds for its values.
Finally, in the chapter's main result, we prove a general property of heterogeneous network games as, due to the previously found bounds, there might be a portion of users whose sensitivity value can be arbitrarily large without affecting the game.

@@

The above set-up creates a Non-atomic Parallel Network Game with tolls where each player will select the edge that minimises their \textit{individual} traffic latency.
We consider two cases where players either react to tolls in a \textit{homogeneous} or a \textit{heterogeneous} manner.

@@

In the heterogeneous case, each player $p$ reacts differently to tolls, presumably due to different money-time sensitivity values.
We describe this by adding a money-sensitivity weight $\alpha(p)$ on the toll costs experienced by the player, making them see the cost of an edge with flow $x_i$ and toll $t_i$ as $c_i(p) = \ell_i(x_i) + \alpha(p) \cdot t_i$.
For a flow $x$ and tolls $t$, each player considers their costs experienced across all links and then selects to use the one (or one of potentially many) with the lowest cost. 
By also assuming that the players are sorted by money-sensitivity, we can describe their heterogeneity by defining a non-decreasing function $\alpha: [0, 1] \rightarrow [0, +\infty]$.
We call $\alpha$ a \textit{distribution function}.
Even though the definition does allow functions that are not upper bounded with $\alpha(1) = +\infty$, we will always assume that $\alpha$ is finite on $[0, 1)$.
%Finally, we will assume that $\alpha(0) > 0$, since, as we'll see in more detail in Lemma \ref{lemma:a_0_0}, allowing many players close to $0$ breaks the pricing game.

@@

			% Edges
			\draw[->, thick] (s) to[bend left=35] node[midway, above] {$2x$} (t);
			\draw[->, thick] (s) to[bend right=35] node[midway, below] {$x + 1$} (t);

@@

Consider a $([2], \ell, \alpha)$ heterogeneous parallel game with links $[2] = \{1, 2\}$ such that $x_1(0), x_2(0) > 0$ with tolls $t = (t_1, t_2)$ assigned to them and  $x(t) = (x_1(t), x_2(t))$ the Nash equilibrium for $t$.
Without loss of generality we assume $t_1 > t_2$ which from Lemma \ref{lemma:latencies_tolls} leads to $\ell_1(x_1(t)) < \ell_2(x_2(t))$.
For the $2$ edges of the game we introduce the term money sensitivity split $\as(t)$ as the value of $\alpha$ for which if any player $p$ has $\alpha(p)=\as(t)$ then that player sees the $2$ edges' total latencies as equal.
More specifically, $\as(t)$ is the value of the distribution function $\alpha$ for which it holds
\[\ell_1(x_1(t)) + \as(t) \cdot t_1 = \ell_2(x_2(t)) + \as(t) \cdot t_2\]
Solving for $\as$ we get
\[\as(t) = \frac{\ell_2(x_2(t)) - \ell_1(x_1(t))}{t_1 - t_2}\]
\\
Before we get into a more formal definition and description of $\as$, it'd help to first discuss the nature of the split that $\as$ captures.
Regardless of whether there exists a player $p$ such that $\alpha(p) = \as(t)$, it still holds that
\begin{itemize}
	\item if $\alpha(p) < \as(t)$ then $\ell_1(x_1(t)) + \alpha(p) \cdot t_1 < \ell_2(x_2(t)) + \alpha(p \cdot) t_2$, thus $p$ is on edge $1$
	\item if $\alpha(p) > \as(t)$ then $\ell_1(x_1(t)) + \alpha(p) \cdot t_1 > \ell_2(x_2(t)) + \alpha(p) \cdot t_2$, thus $p$ is on edge $2$
	\item if $\alpha(p) = \as(t)$ then $\ell_1(x_1(t)) + \alpha(p) \cdot t_1 = \ell_2(x_2(t)) + \alpha(p) \cdot t_2$, thus $p$ is either on edge $1$ or $2$
\end{itemize}
Remember that we have assumed that $t_1 > t_2 \Rightarrow \ell_1(x_1(t)) < \ell_2(x_2(t))$.
Therefore the flow passing through the faster edge $1$ is contained with players where $\alpha(p) \le \as(t)$, while the flow in the cheaper edge $2$ is contained with players where $\alpha(p) \ge \as(t)$.
Since the players are sorted in increasing order according to $\alpha$, it helps to view the players in the first case as the "lower" part of the split and respectively the players in the second case as the "upper" part of the split.
If it helps with the intuition, alternative split labels could be rushed-relaxed or rich-poor.
Table \autoref{table:split_summary} provides of a summary for each part of the split

\begin{table}[h!]
	\centering
	\caption{Summary of properties for the sensitivity split.}
	\begin{tabular}{| c || c | c |}
		\hline
		& $\alpha(p) \le \as(t)$ & $\alpha(p) \ge \as(t)$ \\ \hline
		sensitivity & time $\ge$ money & time $\le$ money \\ \hline
		latency & lower $(\ell_2)$ & higher $(\ell_1)$ \\ \hline
		toll & higher $(t_1)$ & lower $(t_2)$ \\ \hline
		link/edge & low-latency, high-toll $(1)$ & high-latency, low-toll $(2)$ \\ \hline
		$t_1 - t_2$ & lower & higher \\ \hline
		split & lower & upper \\ \hline
	\end{tabular}
	\label{table:split_summary}
\end{table}

Finally to acknowledge that we have arbitrarily handled any players with $\alpha(p) = \as(t)$.
Those players, if any, even though they see both edges with equal total cost, in the optimal flow $x$ they have settled in either edge $1$ or $2$.
We investigate more in depth the relation of $\as$ with the flow in the following Lemmas.
\\[12pt]
We can now formally define $\as$ and prove some of its properties.

@@

\begin{definition}
	\label{definition:split_function}
	Let $(N, \ell, \alpha)$ a heterogeneous parallel game, tolls $t$ where $t_i \ne t_j$ for links $i, j \in N$ and $x(t)$ the Nash equilibrium for $t$.
	We define the \textit{money sensitivity split function} $\as^{(i, j)}: \{t \in \R_+^N|t_i \ne t_j\} \rightarrow (0, +\infty)$ as
	\[\as^{(i, j)}(t) = \frac{\ell_j(x_j(t)) - \ell_i(x_i(t))}{t_i - t_j}\]
\end{definition}

For $t_i = t_j$ any split value will work, so the function is not well-defined for this case.
We will also give a more formal definition to the lower-upper split intuition we described above.
\begin{definition}
	\label{definition:split_lower_upper}
	Let $(N, \ell, \alpha)$ a heterogeneous parallel game, tolls $t$ where $t_i \ne t_j$ for links $i, j \in N$ and $x(t)$ the Nash equilibrium for $t$.
	Assuming w.l.o.g. that $t_i > t_j$, we define as \textit{lower split} the (possibly empty) flow $x_i(t)$ and as \textit{upper split} the (possibly empty) flow $x_j(t)$. 
\end{definition}

@@

At this point in our analysis, we will need to describe the notion of the lowest and highest $\alpha$ value in a flow of players.
In general, since we're working with a Lebesque-measurable flow, it is natural to not bother with distinguishing between a flow $[0, x_1]$ or $[0, x_1)$, as the player $x_1$ can be arbitrarily placed at any link without affecting the game.
In a heterogeneous setting, however, the player's $\alpha(x_1)$ might deterministically put him in a specific link depending on how $\alpha$ is defined, so we need to be careful with our notation.
We will define the $\alpha$ values of a link's flow in a set and then use border bounds which covers both open and closed intervals.

One difficulty we need to consider with this approach are cases where $t_i = t_j$ for some links $i, j \in N$.
For such tolls $t$, even though $x(t)$ is uniquely defined, we get for all players $p$ that $c_i(p) = c_j(p)$, and thus the players in links $i$ and $j$ can be put arbitrarily in any of the two, regardless of the $\alpha$ value.
Even if we attempted to put them orderly, it actually matters which edge we will put first, as the link might have different flow volume resulting in different $\alpha$ values within.
For this reason we will assume our sets contain all possible $\alpha$ values of any player that might use a link.
We therefore loose the information about the actual flow splits among those links and keep only the ones among links with different toll values (and in consequence different latencies, Lemma \ref{lemma:latencies_tolls}).
Still, even with this information loss, we can still observe that
\begin{enumerate}
	\item The notion of $\as$ as the $\alpha$ value that views two links as equal is still valid, since such a player will also view as equal any other link with the same toll value as any of the initial two.
	\item If we limit our scope to only include the links with equal tolls, we actually get a homogeneous sub-game for the total flow in those links.
\end{enumerate}
With the above we arrive at the following definition.

\begin{definition}
	\label{definition:alpha_flow_sets}
	Let $(N, \ell, \alpha)$ a heterogeneous parallel game, tolls $t$ and $x(t)$ the Nash equilibrium for $t$.
	We define as $A_i(t)$ the set of all possible $\alpha(p)$ values of players $p$ using link $i$ in the Nash equilibrium for $t$.
	More formally, we define a set function $A_i: \R_+^N \rightarrow \mathcal{P}(\R_+)$, where $\mathcal{P}(\R_+)$ is the powerset of $\R_+$, such that
	\[A_i(t) = \{\alpha(p)|p \text{ in edge } j \text{ for } x(t) \text{ where } t_j = t_i\}\]
\end{definition}

Notice that with this definition it follows that $A_i(0)$ is the entire domain of $\alpha$ for all $i \in N$.
We continue with describing some basic properties around the values of $\as$.

%We ignore all $\alpha(x_i(0))$ values in order to avoid any confusion, since they are arbitrarily placed in any edge and their $\alpha$ value could change the sets' properties.
%It doesn't affect our analysis, however, since having a split on that player is only possible for $t = 0$ and $\as(0)$ is undefined, plus as we'll show in the next section neither it's limit exists, making the $\alpha$ value of player $x_i(0)$ (in each assumingly split case) irrelevant.

@@

At this point we should notice that $\as$, similarly to $x$, depends only on the toll differences and on the toll ordering of the links.
In order to emphasise on this, let's restrict ourselves to $2$ links and point out that we could alternatively have defined both $x$ and $\as$ as single variable functions with a domain of values $t_d = t_1 - t_2 \in \R$ and function values as such
\[
	x(t_d) =
	\begin{cases*}
		x((t_d, 0)) & $t_d \ge 0$ \\
		x((0, -t_d)) & $t_d < 0$ \\
	\end{cases*}
\]
We will not utilise this definition as is in this work as it gets more complex for games with $n$ links, however displaying it helps with the intuition that the flow, and consequently $\as$, actually changes as the toll differences do in $\R^{N - 1}$.

With that in mind, we will investigate the monotonicity of $\as$ in relation to toll differences (and in extension to latency differences) and only when the ordering does not change.
For this we will need to compare different tolls that create lower-upper splits in the same edges, or in other words for tolls $t, t^\prime$ to hold that if $t_i > t_j$ then also $t_i^\prime > t_j^\prime$ and vice-versa.
We will capture this with the following condition
\begin{equation}
	\label{eq:split_property_cond_tolls_0}
	\frac{t_i - t_j}{t_i^\prime - t_j^\prime} > 0
\end{equation}
where indeed if $t_i > t_j$ then
\[t_i > t_j \Leftrightarrow t_i - t_j > 0 \LeftrightarrowArg{(\ref{eq:split_property_cond_tolls_0})} t_i^\prime - t_j^\prime > 0 \Leftrightarrow t_i^\prime > t_j^\prime\]
and likewise we also get $t_i < t_j \Leftrightarrow t_i^\prime < t_j^\prime$.
Also note that this property also holds for the respective latencies, meaning that if $t$ and $t^\prime$ define the same link toll ordering, then $\frac{\ell_i(x_i(t_i)) - \ell_j(x_j(t_j))}{\ell_i(x_i(t_i^\prime)) - \ell_j(x_j(t_j^\prime))} > 0$.

@@

\begin{proof}
	$ $
	\paragraph{$(i)$}
	Begin by noticing that $\frac{t_i - t_j}{t_i^\prime - t_j^\prime} \le 1 \Rightarrow |t_i - t_j| \le |t_i^\prime - t_j^\prime|$, i.e. from $t$ to $t^\prime$ the toll difference is not decreasing, which means that the players in the upper link (i.e. the players who already prefer the higher latency and lower toll link, non-empty from assumption) will still view their link as the best option.
	Therefore only flow from the lower latency edge, if any, might move towards the slower one.
	Assume w.l.o.g. that $t_i > t_j$, giving us $x_i(t) \ge x_i(t^\prime)$ and $x_j(t) \le x_j(t^\prime)$.

@@

	If $x_i(t) > x_i(t^\prime)$ then there exists a player $p$ who is in link $i$ in the Nash equilibrium for $t$ and in link $j$ for the one for $t^\prime$, meaning that from Definition \ref{definition:alpha_flow_sets} we get
	\[\inf A_j(t^\prime) \le \alpha(p) \le \sup A_i(t)\]
	By now carefully applying  (twice) the property from Lemma $\ref{lemma:split_basic}(iii)$ we get
	\[\as^{(i, j)}(t^\prime) \le \inf A_j(t^\prime) \le \sup A_i(t) \le \as^{(i, j)}(t)\]

	\paragraph{$(ii)$}
	Symmetrically to $(i)$ in this case the toll difference is non-increasing from $t$ to $t^\prime$, and therefore flow from the higher latency edge will move towards the lower one, i.e. $x_i(t) \le x_i(t^\prime)$ and $x_j(t) \ge x_j(t^\prime)$ (assuming again $t_i > t_j$).
	With a similar argument we then get $\as^{(i, j)}(t) \le \as^{(i, j)}(t^\prime)$.

@@

Having now a good overview of the overall values $\as$, we notice that there exist values of $\alpha$ that will never be a value of $\as$.
Do then those values actually affect our game in any way?
We answer this in the theorem below, which is the main result of this chapter, preceded by a lemma to describe those missing values.

@@

\begin{proof}
	All players $p$ with $\alpha(p) = 0$ will completely neglect the toll values and play the congestion game only considering the flow latencies, thus always selecting the fastest edge, regardless of the toll prices.

>>>>

\thispagestyle{empty}
\pagenumbering{gobble}
\chapter*{Abstract}
In this masters thesis we study a $2$-level game where, on an $n$-link network from a source $s$ to a target $t$, a unit of flow wants to move from $s$ to $t$ using the link with the lowest cost, while the link operators compete for profit by assigning tolls to links and thus creating a toll congestion game.
We examine only affine latencies for the links.
In addition, each flow user responds to tolls in a heterogeneous way, i.e. each player $p$ in the flow has a different time-money sensitivity value, which is described by a distribution function $\alpha(p)$.
We first present some definitions and properties of pricing homogeneous games, heavily based on previous work, and using them as base, we extend them to describe pricing games with heterogeneous users.
We introduce a new term, the sensitivity split function $\as(t)$, defined for any $2$ links of the network as the time-money sensitivity value for which, given a set of tolls $t$, the link costs are equal.
With the help of $\as$ we describe some properties around the selfish behaviour of heterogeneous users for different tolls, as well as prove the existence of bounds for the sensitivity values that are relevant to the game.
Then, arriving at the main body of this study, we investigate the existence of a Nash Equilibrium in the profit game between the link operators for different cases of heterogeneous users.
We show there is no Nash Equilibrium when there are many users with $0$ sensitivity, i.e. players not affected by tolls, so we further assume $\alpha(p) > 0$.
We then investigate cases of fixed distribution functions, which, even though create homogeneous behaviour for the users (making them pseudo-heterogeneous games), help us describe how flow, tolls and equilibria behave as that fixed value changes.
Using all the above, we study step distribution functions, where by limiting our scope to $2$ links, we present strict conditions necessary for the existence or not of a Nash Equilibrium in the profit game between the link operators.
We present and analyse an algorithm to calculate that equilibrium, if it exists, and finish with some discussion about potential future work.
\clearpage

@@

In this thesis we study a two level game.
On the basis there is a network with 2 nodes $(s, t)$ and $n$ links, each link directed from $s$ to $t$ and weighted by a non-decreasing latency function that defines how the traffic increases as more players flow into that link.
On the lower level, a flow $[0, 1]$ wants to move from $s$ to $t$ using one of the $n$ links and experience minimum latency (traffic).
On the upper level, each link is managed by a different operator who can assign a toll to their link and gain profit proportional to that toll and the flow that ends up using the link.
The tolls impose an additional cost to the flow players, affecting the lower level game, and the link operators compete with each other to maximise their profit.
In our case we will additionally assume that the flow users behave in a heterogeneous way when it comes to tolls, meaning that each player has a different time-money trade-off and thus see the link costs differently.

The structure of this thesis is as such.
We finish this chapter by briefly presenting previous work in this field, all while examining some of the different models and properties that have been researched in the literature so far.
This will also serve as a bridge to Chapter \ref{chapter:preliminaries} were we will set our basis for the rest of the study.
This includes formal definitions of the models and properties we introduced from previous work, as well as some additional -but still basic- properties of the models, with heavy focus on the user's time-money trade-off, captured by a money-sensitivity distribution function $\alpha$.

Entering the main body of our work, in Chapter \ref{chapter:split} we introduce a new term regarding any two links of the network, called \textit{money-sensitivity split}, which captures the notion of a (potentially non-existent) player whose money-sensitivity makes them view the two links as equal.
We will then analyse that notion and provide properties and bounds for its values.
Finally, in the chapter's main result, we prove a general property of heterogeneous network games as, due to the previously found bounds, there might be a portion of users whose sensitivity value can be arbitrarily large without affecting the game.

@@

The above set-up creates a Non-atomic Parallel Network Game with tolls where each player will select the link that minimises their \textit{individual} traffic latency.
We consider two cases where players either react to tolls in a \textit{homogeneous} or a \textit{heterogeneous} manner.

@@

In the heterogeneous case, each player $p$ reacts differently to tolls, presumably due to different time-money trade-off values.
We describe this by adding a money-sensitivity weight $\alpha(p)$ on the toll costs experienced by a player, making them see the cost of a link with flow $x_i$ and toll $t_i$ as $c_i(p) = \ell_i(x_i) + \alpha(p) \cdot t_i$.
For a flow $x$ and tolls $t$, each player considers their costs experienced across all links and then selects to use the one (or one of potentially many) with the lowest cost. 
By also assuming that the players are sorted by money-sensitivity, we can describe their heterogeneity by defining a non-decreasing function $\alpha: [0, 1] \rightarrow [0, +\infty]$.
We call $\alpha$ a \textit{distribution function}.
Even though the definition does allow functions that are not upper bounded with $\alpha(1) = +\infty$, we will always assume that $\alpha$ is finite on $[0, 1)$.
%Finally, we will assume that $\alpha(0) > 0$, since, as we'll see in more detail in Lemma \ref{lemma:a_0_0}, allowing many players close to $0$ breaks the pricing game.

@@

			% Links
			\draw[->, thick] (s) to[bend left=35] node[midway, above] {$2x$} (t);
			\draw[->, thick] (s) to[bend right=35] node[midway, below] {$x + 1$} (t);

@@

One of the main difficulties with heterogeneity is that, for a given set of tolls, flow users with different money-sensitivity values, view toll values also differently, and therefore, in practice, play different games.
In the analysis of Example \ref{example:simple_alpha} we can find a first glimpse on how to tackle this issue, as we can see that the flow users on each link are organised around the player that views the two link costs as equal.
This notion will be the center of this chapter, and using it we will try and describe some properties about all users.

We start with a simple example in a network with $2$ links.
Consider $([2], \ell, \alpha)$, a heterogeneous parallel game with two links $[2] = \{1, 2\}$ such that $x_1(0), x_2(0) > 0$, tolls $t = (t_1, t_2)$ assigned to them and  $x(t) = (x_1(t), x_2(t))$ the Nash equilibrium for $t$.
Without loss of generality we assume $t_1 > t_2$ which from Lemma \ref{lemma:latencies_tolls} leads to $\ell_1(x_1(t)) < \ell_2(x_2(t))$.
For the $2$ links of the game we introduce the term money sensitivity split $\as(t)$ as the value of $\alpha$ for which if any player $p$ has $\alpha(p)=\as(t)$ then that player views the $2$ links' total costs as equal.
More specifically, $\as(t)$ is the value of the distribution function $\alpha$ for which it holds
\[\ell_1(x_1(t)) + \as(t) \cdot t_1 = \ell_2(x_2(t)) + \as(t) \cdot t_2\]
from which, after solving for $\as(t)$, we get
\[\as(t) = \frac{\ell_2(x_2(t)) - \ell_1(x_1(t))}{t_1 - t_2}\]
\\
Before we get into a more formal definition and description of $\as$, it'd help to first discuss the nature of the split that $\as$ captures.
Regardless of whether there exists a player $p$ such that $\alpha(p) = \as(t)$, it still holds that
\begin{itemize}
	\item if $\alpha(p) < \as(t)$ then $\ell_1(x_1(t)) + \alpha(p) \cdot t_1 < \ell_2(x_2(t)) + \alpha(p \cdot) t_2$, thus $p$ is on link $1$
	\item if $\alpha(p) > \as(t)$ then $\ell_1(x_1(t)) + \alpha(p) \cdot t_1 > \ell_2(x_2(t)) + \alpha(p) \cdot t_2$, thus $p$ is on link $2$
	\item if $\alpha(p) = \as(t)$ then $\ell_1(x_1(t)) + \alpha(p) \cdot t_1 = \ell_2(x_2(t)) + \alpha(p) \cdot t_2$, thus $p$ is either on link $1$ or $2$
\end{itemize}
Remember that we have assumed that $t_1 > t_2 \stackrel{\ref{lemma:latencies_tolls}}{\Leftrightarrow} \ell_1(x_1(t)) < \ell_2(x_2(t))$.
Therefore the flow in the lower-latency link $1$ has players with $\alpha(p) \le \as(t)$, while the flow in the higher-latency link $2$ has players with $\alpha(p) \ge \as(t)$.
Since the players are sorted in increasing order according to $\alpha$, it helps to view the players in the first case as the "lower" part of the split and respectively the players in the second case as the "upper" part of the split.
Alternative split labels could be rushed-relaxed or rich-poor.
\autoref{table:split_summary} provides of a summary of the properties for each part of the split

\begin{table}[h!]
	\centering
	\caption{Summary of properties for the sensitivity split.}
	\begin{tabular}{| c || c | c |}
		\hline
		& \textbf{lower split} & \textbf{upper split} \\ \hline
		$\alpha$ & $\alpha(p) \le \as(t)$ & $\alpha(p) \ge \as(t)$ \\ \hline
		link & low-latency, high-toll & high-latency, low-toll \\ \hline
		sensitivity & time $\ge$ money & time $\le$ money \\ \hline
		%latency & lower $(\ell_1)$ & higher $(\ell_2)$ \\ \hline
		%toll & higher $(t_1)$ & lower $(t_2)$ \\ \hline
		%$t_1 - t_2$ & lower & higher \\ \hline
	\end{tabular}
	\label{table:split_summary}
\end{table}

Finally to acknowledge that we have arbitrarily handled any players with $\alpha(p) = \as(t)$.
Those players, if any, even though they see both links with equal total cost, in the optimal flow $x$ they have settled in either link $1$ or $2$.
We investigate more in depth the relation of $\as$ with the flow in the next propositions.

We can now formally define $\as$ and prove some of its properties.

@@

\begin{definition}
	\label{definition:split_function}
	Let $(N, \ell, \alpha)$ a heterogeneous parallel game, tolls $t$ where $t_i \ne t_j$ for links $i, j \in N$ and $x(t)$ the Nash equilibrium for $t$.
	We define the \textit{money sensitivity split function} $\as^{(i, j)}: \{t \in \R_+^N|t_i \ne t_j\} \rightarrow (0, +\infty)$ as
	\[\as^{(i, j)}(t) = \frac{\ell_j(x_j(t)) - \ell_i(x_i(t))}{t_i - t_j}\]
\end{definition}
We can easily see that if any flow user $p$ has $\alpha(p) = \as^{(i, j)}(t)$ then $c_i(p) = c_j(p)$.
The fact that the function is not well-defined for $t_i = t_j$ matches with the notion we're trying to capture, as in that case we get $c_i(p) = c_j(p)$ for all flow users of the network, regardless of their money-sensitivity value.
We will also give a more formal definition to the lower-upper split intuition we described above.
\begin{definition}
	\label{definition:split_lower_upper}
	Let $(N, \ell, \alpha)$ a heterogeneous parallel game, tolls $t$ where $t_i \ne t_j$ for links $i, j \in N$ and $x(t)$ the Nash equilibrium for $t$.
	Assuming w.l.o.g. that $t_i > t_j$, we define as \textit{lower split} the (possibly empty) flow $x_i(t)$ and as \textit{upper split} the (possibly empty) flow $x_j(t)$. 
\end{definition}

@@

At this point in our analysis, we will need to describe the notion of the lowest and highest $\alpha$ value in a link's flow, which then in turn requires us to look at which interval from the $[0, 1]$ flow is assigned to which link.
We have assumed that the flow is ordered by increasing $\alpha$ values, so from the fact that for any given set of tolls, any toll ordering defines a respective link ordering where the users are assigned again with increasing $\alpha$ values, it follows that a toll ordering can define a partition of $[0, 1]$ where the elements are the intervals of each link.
Example \ref{example:simple_alpha}, for instance, has flow on paths $x(3, 2) = (1/4, 3/4)$ which corresponds to partition $\left[0, \tfrac14\right] \cup \left(\tfrac14, 1\right]$ or $\left[0, \tfrac14\right) \cup \left[\tfrac14, 1\right]$, since player $1/4$ views the two link costs as equal.

Using flow on paths to describe the assignment of flow to links, we inherently ignore the edge players of the respective flow intervals as negligible in a Lebesque-measurable flow.
When looking at $\alpha$ values, however, a player's $\alpha$ value might deterministically put them in a specific link, depending on how $\alpha$ is defined.
If in Example \ref{example:simple_alpha} we consider a different distribution function where $\alpha(p) = 1$ for $p < 1/4$ and $\alpha(p) = 2$ otherwise, we'd still get $x(3, 2) = (1/4, 3/4)$ (checked similarly as in the example's analysis) but with player $1/4$ strictly selecting link $2$ (since $\alpha(1/4) = 2$) and no player viewing the two link costs equally.
We will cover both cases of open and closed intervals by using border bounds on the set of all $\alpha$ values of a link's flow.

One other difficulty we need to consider are cases where $t_i = t_j$ for some links $i, j \in N$.
Remember that $x(t)$ is only uniquely defined with regards to costs, which in extension makes players in such links with equal cost (viewed as such by all players of the game) able to be put arbitrarily in any of the two, regardless of their $\alpha$ value.
Even if we attempted to assume a link assignment ordered by $\alpha$, the link order also matters, as the (equal latency) links might have different flow volume, resulting in different $\alpha$ values in the flow that uses each.
We tackle this by assuming that our sets contain all possible $\alpha$ values of any player that might use that link.
We therefore ignore the information about the actual flow splits among those links and keep only the ones among links with different toll values (and in consequence different latencies, Lemma \ref{lemma:latencies_tolls}).
%Still, even with this information loss, we observe that
%\begin{enumerate}
%	\item The notion of $\as$ as the $\alpha$ value that views two links as equal is still valid, since such a player will also view as equal any other link with the same toll value as any of the initial two.
%	\item If we limit our scope to only include the links with equal tolls, we actually get a homogeneous sub-game for the total flow in those links.
%\end{enumerate}

With all the above we arrive at the following definition.

\begin{definition}
	\label{definition:alpha_flow_sets}
	Let $(N, \ell, \alpha)$ a heterogeneous parallel game, tolls $t$ and $x(t)$ the Nash equilibrium for $t$.
	We define as $A_i(t)$ the set of all possible $\alpha(p)$ values of players $p$ using link $i$ in the Nash equilibrium for $t$.
	More formally, we define a set function $A_i: \R_+^N \rightarrow \mathcal{P}(\R_+)$, where $\mathcal{P}(\R_+)$ is the powerset of $\R_+$, such that
	\[A_i(t) = \{\alpha(p) | f(p) = j \wedge t_j = t_i\}\]
\end{definition}

Notice that with this definition it follows that $A_i(0)$ is the entire domain of $\alpha$ for any $i \in N$.
We continue with describing some basic properties around the values of $\as$.

%We ignore all $\alpha(x_i(0))$ values in order to avoid any confusion, since they are arbitrarily placed in any link and their $\alpha$ value could change the sets' properties.
%It doesn't affect our analysis, however, since having a split on that player is only possible for $t = 0$ and $\as(0)$ is undefined, plus as we'll show in the next section neither it's limit exists, making the $\alpha$ value of player $x_i(0)$ (in each assumingly split case) irrelevant.

@@

At this point we should notice that $\as$, similarly to $x$, depends only on the toll differences and on the toll ordering of the links.
In order to emphasise on this, let's restrict ourselves to $2$ links and point out that we could alternatively have defined both $x$ and $\as$ as single variable functions with a domain of values $t_d = t_1 - t_2 \in \R$ and function values as such
\[
	x(t_d) =
	\begin{cases*}
		x(t_d, 0) & $t_d \ge 0$ \\
		x(0, -t_d) & $t_d < 0$ \\
	\end{cases*}
\]
We will not utilise this definition as is in this work as it gets more complex for games with $n$ links, however displaying it helps with the intuition that the flow, and consequently $\as$, actually changes as the toll differences do in $\R^{N - 1}$.

With that in mind, we will investigate the monotonicity of $\as$ in relation to toll differences (and in extension to latency differences) and only when the ordering does not change.
For this we will need to compare different tolls that create lower-upper splits in the same links, or in other words for tolls $t, t^\prime$ to hold that if $t_i > t_j$ then also $t_i^\prime > t_j^\prime$ and vice-versa.
We will capture this with the following condition
\begin{equation}
	\label{eq:split_property_cond_tolls_0}
	\frac{t_i - t_j}{t_i^\prime - t_j^\prime} > 0
\end{equation}
where indeed if $t_i > t_j$ then
\[t_i > t_j \Leftrightarrow t_i - t_j > 0 \LeftrightarrowArg{(\ref{eq:split_property_cond_tolls_0})} t_i^\prime - t_j^\prime > 0 \Leftrightarrow t_i^\prime > t_j^\prime\]
and likewise we also get $t_i < t_j \Leftrightarrow t_i^\prime < t_j^\prime$.
Also note that this property also holds for the respective latencies, meaning that if $t$ and $t^\prime$ define the same toll ordering on links, then $\frac{\ell_i(x_i(t_i)) - \ell_j(x_j(t_j))}{\ell_i(x_i(t_i^\prime)) - \ell_j(x_j(t_j^\prime))} > 0$.

@@

\begin{proof}
	$ $
	\paragraph{$(i)$}
	Begin by noticing that $\frac{t_i - t_j}{t_i^\prime - t_j^\prime} \le 1 \Rightarrow |t_i - t_j| \le |t_i^\prime - t_j^\prime|$, i.e. from $t$ to $t^\prime$ the toll difference is not decreasing, which means that the players in the upper link (i.e. the players who already prefer the higher latency and lower toll link, non-empty from assumption) will still view their link as the best option.
	Therefore only flow from the lower latency link, if any, might move towards the slower one.
	Assume w.l.o.g. that $t_i > t_j$, giving us $x_i(t) \ge x_i(t^\prime)$ and $x_j(t) \le x_j(t^\prime)$.

@@

	If $x_i(t) > x_i(t^\prime)$ then there exists a player $p$ who is in link $i$ in the Nash equilibrium for $t$ and in link $j$ for the one for $t^\prime$, meaning that by applying (twice) Definition \ref{definition:alpha_flow_sets} we get
	\[\inf A_j(t^\prime) \le \alpha(p) \le \sup A_i(t)\]
	By now carefully applying  (twice) the property from Lemma $\ref{lemma:split_basic}(iii)$ we get
	\[\as^{(i, j)}(t^\prime) \le \inf A_j(t^\prime) \le \sup A_i(t) \le \as^{(i, j)}(t)\]

	\paragraph{$(ii)$}
	Arguing symmetrically to $(i)$, we see that in this case the toll difference is non-increasing from $t$ to $t^\prime$, and therefore flow from the higher latency link will move towards the lower one, i.e. $x_i(t) \le x_i(t^\prime)$ and $x_j(t) \ge x_j(t^\prime)$ (assuming again $t_i > t_j$).
	With a similar argument we then get $\as^{(i, j)}(t) \le \as^{(i, j)}(t^\prime)$.

@@

Having now a good overview of the overall values of $\as$, we notice that there exist values of $\alpha$ that will never be a value of $\as$.
Do then those values actually affect our game in any way?
We answer this in the theorem below, which is the main result of this chapter, preceded by a lemma to describe those missing values.

@@

\begin{proof}
	All players $p$ with $\alpha(p) = 0$ will completely neglect the toll values and play the congestion game only considering the flow latencies, thus always selecting the fastest link, regardless of the toll prices.
